Model LF

### 2022-09-30 max_dp endogen stød.Rmd
commit

```{r}
u=yk/(bd_nfc_k+equip_nfc_k) #Rate of capacity utilization
prate=s_nf/(stats::lag(bd_nfc,-1)+stats::lag(equip_nfc,-1)) # Profit rate
```

@@

## u_ds
reg_5 = lm(u~ sd1+ sd2 + sd3)

u_ds= reg_5$residuals + mean(u)

@@

@@

COMMENT> 
BEHAVIORAL> i_equip_nfc_k_ds
TSRANGE 2006 1 2020 1
EQ> LOG(i_equip_nfc_k_ds) = p_807 + p_808 * TSDELTALOG(TSLAG(i_equip_nfc_k_ds,1)/TSLAG(equip_nfc_k,2)) + p_809 * TSDELTALOG(ps_ds) + p_810 * TSDELTALOG(u_ds) + p_811 *  LOG(TSLAG(i_equip_nfc_k_ds,1)/TSLAG(equip_nfc_k,2)) + p_812 * LOG(TSLAG(ps_ds,1)) + p_813 * LOG(TSLAG(u_ds,1)) + p_814 * dummy_10 + p_815 * dummy_11 + p_890*TSDELTALOG(tobinq) + p_891*LOG(TSLAG(tobinq,1)) + alpha_1*TSLAG(LOG(i_equip_nfc_k_ds),1) + alpha_2*TSLAG(LOG(equip_nfc_k),1) + alpha_3*TSLAG(-LOG(equip_nfc_k),2)
COEFF> p_807 p_808 p_809 p_810 p_811 p_812 p_813 p_814 p_815 p_890 p_891 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1
STORE> coe(11)

@@

  ws = TIMESERIES(c(ws),   
                  START=c(2005,2),FREQ=4),
  ps = TIMESERIES(c(ps),   
                  START=c(2005,2),FREQ=4),
  u = TIMESERIES(c(u),   
                 START=c(2005,2),FREQ=4),
  prate = TIMESERIES(c(prate),   
                     START=c(2005,3),FREQ=4),
  tobinq = TIMESERIES(c(tobinq),   
                      START=c(2005,2),FREQ=4),

@@

#S_modelData$wage_growth = wage_growth

@@

```{r, echo=FALSE}
wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_t_00 = S_model$simulation$wage_ds_t
wage_growth_00 = S_model$simulation$wage_growth

@@

u_00 = S_model$simulation$u

@@

@@

tilpas_pr_01b = Shock_1b$simulation$tilpas_pr

part_01b = Shock_1b$simulation$part
nben_h_01b = Shock_1b$simulation$nben_h
wage_ds_01b = Shock_1b$simulation$wage_ds
dp_person_01b = Shock_1b$simulation$dp_person

@@

i_equip_nfc_k_ds_05 = Shock_5$simulation$i_equip_nfc_k_ds

@@

@@

yk_ds_06 = Shock_6$simulation$yk_ds
emp_06 = Shock_6$simulation$emp
wage_ds_06 = Shock_6$simulation$wage_ds
ur_ds_06 = Shock_6$simulation$ur_ds
pc_ds_06 = Shock_6$simulation$pc_ds
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
pconk_ds_06 = Shock_6$simulation$pconk_ds
komp_r_06 = Shock_6$simulation$komp_r
max_dp_06 = Shock_6$simulation$max_dp
nben_h_06 = Shock_6$simulation$nben_h
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
ik_06 = Shock_6$simulation$ik
wage_ds_t_06 = Shock_6$simulation$wage_ds_t
nben_h_un_06 = Shock_6$simulation$nben_h_un
nl_g_06 = Shock_6$simulation$nl_g
nsben_h_06 = Shock_6$simulation$nsben_h
dp_person_06 = Shock_6$simulation$dp_person
part1_06 = Shock_6$simulation$part1

@@

plot(komp_r_06, col= "red"); lines(komp_r_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

yk_ds_07 = Shock_7$simulation$yk_ds
emp_07 = Shock_7$simulation$emp
wage_ds_07= Shock_7$simulation$wage_ds
ur_ds_07 = Shock_7$simulation$ur_ds
pc_ds_07 = Shock_7$simulation$pc_ds
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
pconk_ds_07 = Shock_7$simulation$pconk_ds
komp_r_07 = Shock_7$simulation$komp_r
max_dp_07 = Shock_7$simulation$max_dp
nben_h_07 = Shock_7$simulation$nben_h
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
ik_07 = Shock_7$simulation$ik
wage_ds_t_07 = Shock_7$simulation$wage_ds_t
nben_h_un_07 = Shock_7$simulation$nben_h_un
nl_g_07 = Shock_7$simulation$nl_g
nsben_h_07 = Shock_7$simulation$nsben_h
dp_person_07 = Shock_7$simulation$dp_person

shock_kuld_07 = Shock_7$simulation$shock_kuld

@@

@@

```{r}
plot((net_export_05 / net_export_00), col= "red");
legend("top", legend=c("Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

@@

```{r}
plot((yk_ds_01b / yk_ds_00), col= "red", ylim= c(0.995,1.005));
lines((yk_ds_05 / yk_ds_00), col= "blue");
lines((yk_ds_06 / yk_ds_00), col= "green");
lines((yk_ds_07 / yk_ds_00), col= "orange");
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

>>>>

```{r}
prate=s_nf/(stats::lag(bd_nfc,-1)+stats::lag(equip_nfc,-1)) # Profit rate
```

@@

@@

u_ds=yk_ds/(bd_nfc_k+equip_nfc_k) #Rate of capacity utilization

@@

COMMENT> 
BEHAVIORAL> i_equip_nfc_k_ds
TSRANGE 2006 1 2020 1
EQ> LOG(i_equip_nfc_k_ds) = p_807 +
p_808 * TSDELTALOG(TSLAG(i_equip_nfc_k_ds,1)/TSLAG(equip_nfc_k,2)) +
p_811 * LOG(TSLAG(i_equip_nfc_k_ds,1)/TSLAG(equip_nfc_k,2)) +
p_812 * LOG(TSLAG(ps_ds,1)) +
p_813 * LOG(TSLAG(u_ds,1)) +
p_814 * dummy_10 +
p_815 * dummy_11 +
p_890*TSDELTALOG(tobinq) +
p_891*LOG(TSLAG(tobinq,1)) +
alpha_1*TSLAG(LOG(i_equip_nfc_k_ds),1) +
alpha_2*TSLAG(LOG(equip_nfc_k),1) +
alpha_3*TSLAG(-LOG(equip_nfc_k),2)
COEFF> p_807 p_808 p_811 p_812 p_813 p_814 p_815 p_890 p_891 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1
STORE> coe(11)

@@

  ws = TIMESERIES(c(ws),   
                  START=c(2005,2),FREQ=4),
  ps = TIMESERIES(c(ps),   
                  START=c(2005,2),FREQ=4),
  prate = TIMESERIES(c(prate),   
                     START=c(2005,3),FREQ=4),
  tobinq = TIMESERIES(c(tobinq),   
                      START=c(2005,2),FREQ=4),

@@

#S_modelData$u_ds = u_ds

@@

```{r, echo=FALSE}
wage_trim_00 = S_model$simulation$wage_trim
dp_person_00 = S_model$simulation$dp_person
max_dp_00 = S_model$simulation$max_dp
stat_tilpas_00 = S_model$simulation$stat_tilpas
stat_reg_00= S_model$simulation$stat_tilpas
tilpas_pr_00 = S_model$simulation$tilpas_pr
wage_gap1_00 = S_model$simulation$wage_gap1
wage_ds_t_00 = S_model$simulation$wage_ds_t
u_ds_00 = S_model$simulation$u_ds

@@

@@

plot(u_ds_00, col= "green"); lines(u_ds, col = "blue"); 
legend("top",legend=c("Baseline", "Real data"),lty=c(1,1),lwd=c(2),bty="n", col = c("green", "blue"));
grid()

@@

tilpas_pr_01b = Shock_1b$simulation$tilpas_pr
u_ds_01b = Shock_1b$simulation$u_ds
part_01b = Shock_1b$simulation$part
nben_h_01b = Shock_1b$simulation$nben_h
wage_ds_01b = Shock_1b$simulation$wage_ds
dp_person_01b = Shock_1b$simulation$dp_person

@@

i_equip_nfc_k_ds_05 = Shock_5$simulation$i_equip_nfc_k_ds
u_ds_05 = Shock_5$simulation$u_ds

@@

plot(u_ds_05, col= "red"); lines(u_ds_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

yk_ds_06 = Shock_6$simulation$yk_ds
emp_06 = Shock_6$simulation$emp
wage_ds_06 = Shock_6$simulation$wage_ds
ur_ds_06 = Shock_6$simulation$ur_ds
pc_ds_06 = Shock_6$simulation$pc_ds
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
pconk_ds_06 = Shock_6$simulation$pconk_ds
komp_r_06 = Shock_6$simulation$komp_r
max_dp_06 = Shock_6$simulation$max_dp
nben_h_06 = Shock_6$simulation$nben_h
yd_hk_ds_06 = Shock_6$simulation$yd_hk_ds
ik_06 = Shock_6$simulation$ik
wage_ds_t_06 = Shock_6$simulation$wage_ds_t
nben_h_un_06 = Shock_6$simulation$nben_h_un
nl_g_06 = Shock_6$simulation$nl_g
nsben_h_06 = Shock_6$simulation$nsben_h
dp_person_06 = Shock_6$simulation$dp_person
part1_06 = Shock_6$simulation$part1
u_ds_06 = Shock_6$simulation$u_ds

@@

plot(komp_r_06, col= "red"); lines(komp_r_00, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(u_ds_06, col= "red"); lines(u_ds_05, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

yk_ds_07 = Shock_7$simulation$yk_ds
emp_07 = Shock_7$simulation$emp
wage_ds_07= Shock_7$simulation$wage_ds
ur_ds_07 = Shock_7$simulation$ur_ds
pc_ds_07 = Shock_7$simulation$pc_ds
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
pconk_ds_07 = Shock_7$simulation$pconk_ds
komp_r_07 = Shock_7$simulation$komp_r
max_dp_07 = Shock_7$simulation$max_dp
nben_h_07 = Shock_7$simulation$nben_h
yd_hk_ds_07 = Shock_7$simulation$yd_hk_ds
ik_07 = Shock_7$simulation$ik
wage_ds_t_07 = Shock_7$simulation$wage_ds_t
nben_h_un_07 = Shock_7$simulation$nben_h_un
nl_g_07 = Shock_7$simulation$nl_g
nsben_h_07 = Shock_7$simulation$nsben_h
dp_person_07 = Shock_7$simulation$dp_person
u_ds_07 = Shock_7$simulation$u_ds
shock_kuld_07 = Shock_7$simulation$shock_kuld

@@

plot(u_ds_07, col= "red"); lines(u_ds_06, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

@@

```{r}
plot((ik_05 / ik_00), col= "red");
legend("top", legend=c("Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

```{r}
plot((pconk_ds_05 / pconk_ds_00), col= "red");
legend("top", legend=c("Wage growth"),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

@@

```{r}
plot((yk_ds_01b / yk_ds_00), col= "red", ylim= c(0.998,1.0015));
lines((yk_ds_05 / yk_ds_00), col= "blue");
lines((yk_ds_06 / yk_ds_00), col= "green");
lines((yk_ds_07 / yk_ds_00), col= "orange");
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

```{r}
plot((u_ds_01b / u_ds_00), col= "red", ylim= c(0.998,1.0015));
lines((u_ds_05 / u_ds_00), col= "blue");
lines((u_ds_06 / u_ds_00), col= "green");
lines((u_ds_07 / u_ds_00), col= "orange");
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```
